Forecasting short-term hourly Emergency Departement arrivals

### 2021-11-03 paper/paper.Rmd

# Result and discussion {#result}

>>>>

Finally, we have calculated the computational time for one iteration on the first rolling origin to compare the speed of each function. All functions were re-estimated on each iteration. ADAM and Poisson regression estimated the parameters taking as the pre-initials the ones obtained in the initial model application to the data in the first origin. This allowed to speed up the computation for these two models. The initial estimation of ADAM took approximately one hour and 25 minutes. Each step in the experiment took the time shown below.
